Liveness-Based Garbage Collection for Lazy Languages

### 2015-06-08 paper/paper.tex
Some problem

\documentclass[9pt]{sigplanconf}
\usepackage{etex}
\usepackage{float}
\usepackage{mathrsfs}
\usepackage{booktabs}
\usepackage{boxedminipage}
\usepackage[T1]{fontenc}
%\usepackage[pdf]{pstricks}
\usepackage{epsfig}
\usepackage{multirow}
\usepackage{url}
\usepackage[normalem]{ulem}
\usepackage{schemepgm}
\usepackage{graphicx}
\usepackage{graphpap}
\usepackage{tabularx}
\usepackage [plain,noend,noline,boxed]{algorithm2e}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{pstricks}
\usepackage{pst-text}
\usepackage{pst-node}
\usepackage{pst-tree}
\usepackage{pst-rel-points}
\usepackage{bcprules}
%\usepackage{program}
\usepackage{algorithmic}

\input{fh_defs}
\def\drawplusplus#1#2#3{\hbox to 0pt{\hbox to #1{\hfill\vrule height #3 depth
      0pt width #2\hfill\vrule height #3 depth 0pt width #2\hfill
      }}\vbox to #3{\vfill\hrule height #2 depth 0pt width
      #1 \vfill}}
      %Poor man's typography
\def\concat{\mathrel{\drawplusplus {12pt}{0.4pt}{5pt}}}
      %It would be better to specify these in font-relative measures, but it
      %probably doesn't scale anyway.
\newcommand{\mycomment}[1]{}
\definecolor{Myblue}{rgb}{.2,0,1}
\newcommand{\comment}[1]{{\color{Myblue}{(#1)}}}
\newcommand{\cred}[1]{{\color{red}{#1}}}
\newcommand{\alan}[1]{{\color{red}{\medskip \hrule\medskip
    #1 \medskip \hrule \medskip}}}
\newcommand{\blankout}[1]{}

%\newcommand{\deltacall}[3]{\delta_{#1}({#2},{#3})}
\newcommand{\scmin} {\mbox{\sf\em in}}
\newcommand{\scmnull}{\mbox{\sf\em null?}}
\newcommand{\scmpair}{\mbox{\sf\em pair?}}
\newcommand{\scmprim}{\ensuremath{\mathsf{+}}}
\newcommand{\sh}[1]{{\colorbox{gray!20}{\framebox{$#1$}}}}
\def\myvec{\mathaccent"017E } % wretched springer mode redefines \vec as bold!
\newcommand{\stk}{\mbox{S}}       % stack
\newcommand{\ID}{\mbox{$\mathbf{ id}$}} % identity function
\newcommand{\bang}{\mbox{\sc bang}}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{lemma}[theorem]{Lemma}
\begin{document}
% --- Author Metadata here ---
\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Liveness-Based Garbage Collection for Lazy Languages}

% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.
\cmt{{
\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors
section.
%
\author{
% 1st. author
\alignauthor K. Prasanna Kumar \\
       \affaddr{IIT Bombay,}\\
       \affaddr{Mumbai 400076, India}
       \email{prasanna@cse.iitb.ac.in}
% 2nd. author
\alignauthor Amey Karkare\\
       \affaddr{IIT Kanpur}\\
       \affaddr{Kanpur 208016, India}
       \email{karkare@cse.iitk.ac.in}
% 3rd. author
\alignauthor Amitabha Sanyal \\
       \affaddr{IIT Bombay}\\
       \affaddr{Mumbai 400076, India}\\
       \email{as@cse.iitb.ac.in}
}
}}
\authorinfo{Double Blind Review}{}{}
\maketitle

@@

The      $\mathit{ref}$     rule      for     \CONS,      shown     in
Figure~\ref{fig:live-judge},  requires   us  to  remove   the  leading
\acar\ and \acdr\  from the access paths in  $\sigma$.  Similarly, the
rules for  \CAR, \CDR, \PRIM, \NULLQ,  and \SIF\ require  us to return
$\emptyset$, if  $\sigma$ itself $\emptyset$.  To  realize these rules
$\sigma$ needs to be known. This creates difficulties since we want to
solve the equations arising out of liveness symbolically.

@@

%------------------------------------------------------------%
\subsubsection{From CFGs to GC-ready DFAs}
\label{sec:NFA-approx}
 We use  the algorithm by Mohri  and Nederhof~\cite{mohri00regular} to
 approximate a CFG to a {\em strongly regular\/} grammar.  The grammar
 fragment  that  defines  the  non-terminal  $\var{\Df{\length}{1}}$
   after the Mohri-Nederhof transformation becomes:

 \begin{eqnarray*} 
   \var{\Df{\length}{1}} &\rightarrow& \clazy\var{\Df{\length}{1'}} \mid
   \acdr\var{\Df{\length}{1}}
   \mid \clazy\var{\Df{\length}{1}}\\
   \var{\Df{\length}{1'}} &\rightarrow& \clazy\var{\Df{\length}{1'}} \mid \epsilon \\
   \langle {\sigma_{\length}} \rangle
   &\rightarrow&
   \epsilon  \mid \clazy\langle{\sigma_{\length}}\rangle
 \end{eqnarray*}

The grammar after the Mohri-Nederhoff transformation is converted into
a  set of  NFAs,  one for  each  $\var{\Lanv{i}{x}}$. We  now apply  the
$\hookrightarrow$ simplification  by repeatedly introducing $\epsilon$
edges to  bypass a pair  of consecutive edges labelled  \bcar\acar\ or
\bcdr\acdr  and  deriving  the  $\epsilon$-closure  of  the  resulting
automaton.   The   process  is  continued   till  a  fixed   point  is
reached.  Finally we  replace  the $\clazy$  edges  by $\epsilon$  and
determinize the automaton thus formed.

%------------------------------------------------------------%
\subsubsection{Transforming NFAs to Accept Forward Paths:}
%\label{sec:NFA-elim}
The   strongly  regular   CFGs  obtained   after   the  Mohri-Nederhof
transformation are first converted into NFAs.  The algorithm described
in  Figure~\ref{algo:simplify-NFA} converts  an NFA  \ntbar\ to  a NFA
\nt\    such    that   $\lang{\ntbar}    \stackrel{*}{\hookrightarrow}
\lang{\nt}$, where {\nt} accepts forward paths only.  \comment{Rewrite
  the algorithm to handle \clazy\  and update the example automata} Thus
\nt\ can be used to check membership of forward paths.

\begin{figure*}[t]
%% \begin{boxedminipage}{.5\textwidth}
%% \begin{center}
%%   \raggedright  {\bf  Input:}  NFA \ntbar\  with  underlying
%%   alphabet $\lbrace \acar, \acdr, \bcar, \bcdr\rbrace$ \\
%% %
%%   \raggedright{\bf Output:} NFA  \nt\ with  underlying
%%   alphabet $\lbrace \acar, \acdr \rbrace$ such that
%%   $\lang{\ntbar} \stackrel{*}{\hookrightarrow} \lang{\nt}$.
%%   \\

@@

%%    \STATE $\nt \leftarrow \nt_i$
%%   \STATE delete all edges with label \bcar\ or \bcdr\ in \nt.
%%  \end{algorithmic}
%% \end{center}
%% \end{boxedminipage}
\begin{boxedminipage}{.5\textwidth}
The algorithm repeatedly introduces  $\epsilon$ edges to bypass a pair
of consecutive edges labelled  \bcar\acar\ or \bcdr\acdr.  The process
is continued till  a fixed point is reached.  When  the fixed point is
reached,   the  resulting   NFA  contains   all   possible  reductions
corresponding to all the paths in the original NFA.  The proofs of the
termination and correctness of  th The algorithm repeatedly introduces
$\epsilon$  edges  to bypass  a  pair  of  consecutive edges  labelled
\bcar\acar\  or \bcdr\acdr.   The process  is continued  till  a fixed
point is reached.  When the  fixed point is reached, the resulting NFA
contains all possible reductions corresponding to all the paths in the
original NFA.  The proofs of the termination and correctness of th The
algorithm repeatedly  introduces $\epsilon$ edges to bypass  a pair of
consecutive edges labelled \bcar\acar\  or \bcdr\acdr.  The process is
continued  till a fixed  point is  reached.  When  the fixed  point is
reached,   the  resulting   NFA  contains   all   possible  reductions
corresponding to all the paths in the original NFA.  The proofs of the
termination and correctness of  th The algorithm repeatedly introduces
$\epsilon$  edges  to bypass  a  pair  of  consecutive edges  labelled
\bcar\acar\  or \bcdr\acdr.   The process  is continued  till  a fixed
point is reached.  When the  fixed point is reached, the resulting NFA
contains all possible reductions corresponding to all the paths in the
original NFA.  The proofs of the termination and correctness of th

\end{boxedminipage}
 \caption{Algorithm for transforming an NFA to  accept forward
   paths only.}\label{algo:simplify-NFA} \figrule
\end{figure*}

The algorithm repeatedly introduces  $\epsilon$ edges to bypass a pair
of consecutive edges labelled  \bcar\acar\ or \bcdr\acdr.  The process
is continued till  a fixed point is reached.  When  the fixed point is
reached,   the  resulting   NFA  contains   all   possible  reductions
corresponding to all the paths in the original NFA.  The proofs of the
termination and correctness  of the algorithm are given  in an earlier
paper~\cite{karkare07liveness}.

%%\input{liveness-dfa.tex}
\comment{change according  to example} We illustrate  the algorithm in
Figure~\ref{algo:simplify-NFA}  by   constructing  the  automaton  for
\var{\Lanv{9}{y}}.   Figure~\ref{fig:automata-construction}  (c) shows
the  automaton  for  \var{\Lanv{9}{y}}  constructed by  composing  the
automata   for    \var{\Uf{\append}{1}},   \var{\Df{\append}{1}}   and
$(\epsilon \mid \acdr \mid \acdr\acar\sigma_{\mathit{\!all}})$.  After
$\epsilon$ removal we get (d). We add an $\epsilon$ edge from $q_2$ to
$q_3$ bypassing the  \bcdr\acdr\ pair from $q_2$ to  $q_2$ and then to
$q_3$. This  is shown in (e).   The $\epsilon$ edge is  removed in (f)
and  a second  $\epsilon$  is  added to  the  automaton bypassing  the
\bcar\acar\ pair  from $q_1$ to $q_2$.  Removing  this $\epsilon$ edge
gives  the automaton  shown  in (g).   Restricting  this automaton  to
forward edges  only, we  get the final  automaton shown in  (h).  This
automaton  recognizes  $\acdr^{*}\!\mid\acdr^{*}\acar  \sigma_{\mathit
  \!all}$, showing  that the entire list \py,  including its elements,
is live at $\pi_9$. Also note  that the language accepted by the final
automaton satisfies the prefix-closed property.

\hrule
\hrule

\section{Implementation}
% GC assumptions
\cred{Introduction}

>>>>

\documentclass[9pt]{sigplanconf}
\usepackage{etex}
\usepackage{float}
\usepackage{mathrsfs}
\usepackage{booktabs}
\usepackage{boxedminipage}
\usepackage[T1]{fontenc}
%\usepackage[pdf]{pstricks}
\usepackage{epsfig}
\usepackage{multirow}
\usepackage{url}
\usepackage[normalem]{ulem}
\usepackage{schemepgm}
\usepackage{graphicx}
\usepackage{graphpap}
\usepackage{tabularx}
\usepackage [plain,noend,noline,boxed]{algorithm2e}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{pstricks}
\usepackage{pst-text}
\usepackage{pst-node}
\usepackage{pst-tree}
\usepackage{pst-rel-points}
\usepackage{bcprules}
%\usepackage{program}
\usepackage{algorithmic}
\input{fh_defs}
\def\drawplusplus#1#2#3{\hbox to 0pt{\hbox to #1{\hfill\vrule height #3 depth
      0pt width #2\hfill\vrule height #3 depth 0pt width #2\hfill
      }}\vbox to #3{\vfill\hrule height #2 depth 0pt width
      #1 \vfill}}
      %Poor man's typography
\def\concat{\mathrel{\drawplusplus {12pt}{0.4pt}{5pt}}}
      %It would be better to specify these in font-relative measures, but it
      %probably doesn't scale anyway.
\newcommand{\mycomment}[1]{}
\definecolor{Myblue}{rgb}{.2,0,1}
\newcommand{\comment}[1]{{\color{Myblue}{(#1)}}}
\newcommand{\cred}[1]{{\color{red}{#1}}}
\newcommand{\alan}[1]{{\color{red}{\medskip \hrule\medskip
    #1 \medskip \hrule \medskip}}}
\newcommand{\blankout}[1]{}

%\newcommand{\deltacall}[3]{\delta_{#1}({#2},{#3})}
\newcommand{\scmin} {\mbox{\sf\em in}}
\newcommand{\scmnull}{\mbox{\sf\em null?}}
\newcommand{\scmpair}{\mbox{\sf\em pair?}}
\newcommand{\scmprim}{\ensuremath{\mathsf{+}}}
\newcommand{\sh}[1]{{\colorbox{gray!20}{\framebox{$#1$}}}}
\def\myvec{\mathaccent"017E } % wretched springer mode redefines \vec as bold!
\newcommand{\stk}{\mbox{S}}       % stack
\newcommand{\ID}{\mbox{$\mathbf{ id}$}} % identity function
\newcommand{\bang}{\mbox{\sc bang}}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{lemma}[theorem]{Lemma}
\begin{document}

% --- Author Metadata here ---
\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Liveness-Based Garbage Collection for Lazy Languages}
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.
%\cmt{{
%\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors
section.
%
\author{
% 1st. author
\alignauthor K. Prasanna Kumar \\
       \affaddr{IIT Bombay,}\\
       \affaddr{Mumbai 400076, India}
       \email{prasanna@cse.iitb.ac.in}
% 2nd. author
\alignauthor Amey Karkare\\
       \affaddr{IIT Kanpur}\\
       \affaddr{Kanpur 208016, India}
       \email{karkare@cse.iitk.ac.in}
% 3rd. author
\alignauthor Amitabha Sanyal \\
       \affaddr{IIT Bombay}\\
       \affaddr{Mumbai 400076, India}\\
       \email{as@cse.iitb.ac.in}
}
}}
\authorinfo{Double Blind Review}{}{}
\maketitle

@@

The      $\mathit{ref}$     rule      for     \CONS,      shown     in
Figure~\ref{fig:live-judge},  requires   us  to  remove   the  leading
\acar\ and \acdr\  from the access paths in  $\sigma$.  Similarly, the
rules for  \CAR, \CDR, \PRIM, \NULLQ,  and \SIF\ require  us to return
$\emptyset$, if  $\sigma$ itself is $\emptyset$.  To  realize these rules
$\sigma$ needs to be known. This creates difficulties since we want to
solve the equations arising out of liveness symbolically.

@@

%------------------------------------------------------------%
\subsubsection{From CFGs to GC-ready DFAs}
\label{sec:NFA-approx}
 We use  the algorithm by Mohri  and Nederhof~\cite{mohri00regular} to
 approximate a CFG to a {\em strongly regular\/} grammar.  For
 example, the grammar
 fragment  for  the  non-terminal  $\var{\Df{\length}{1}}$  after  the
 Mohri-Nederhof transformation is:
 \begin{eqnarray*} 
   \var{\Df{\length}{1}} &\rightarrow& \clazy\var{\Df{\length}{1'}} \mid
   \acdr\var{\Df{\length}{1}} 
   \mid \clazy\var{\Df{\length}{1}}\\
   \var{\Df{\length}{1'}} &\rightarrow& \clazy\var{\Df{\length}{1'}}
   \mid \epsilon      
 \end{eqnarray*}

The strongly regular grammar is converted into a set of
NFAs,   one  for   each  $\var{\Lanv{i}{x}}$.   The  $\hookrightarrow$
simplification  is now  done  on the  NFAs  by repeatedly  introducing 
$\epsilon$  edges  to  bypass  pairs  of  consecutive  edges  labelled
\bcar\acar\ or \bcdr\acdr\  and constructing the
$\epsilon$-closure. Since the $\epsilon$-closure step may create more
adjacent \bcar\acar\ and \bcdr\acdr\  edges, the simplification is  
 continued  till a  fixed point is  reached. The algorithm  for this
appears  in~\cite{asati14lgc},   Figure[].  Finally  we   replace  the
$\clazy$  edges  by  $\epsilon$  and determinize  the  automaton  thus
formed.

\comment{A paragraph more to explain the illustration on the following lines:

%------------------------------------------------------------%
%% \subsubsection{Transforming NFAs to Accept Forward Paths:}
%% %\label{sec:NFA-elim}
%% The   strongly  regular   CFGs  obtained   after   the  Mohri-Nederhof
%% transformation are first converted into NFAs.  The algorithm described
%% in  Figure~\ref{algo:simplify-NFA} converts  an NFA  \ntbar\ to  a NFA
%% \nt\    such    that   $\lang{\ntbar}    \stackrel{*}{\hookrightarrow}
%% \lang{\nt}$, where {\nt} accepts forward paths only.  \comment{Rewrite
%%   the algorithm to handle \clazy\  and update the example automata} Thus
%% \nt\ can be used to check membership of forward paths.

%%\begin{figure*}[t]
%% \begin{boxedminipage}{.5\textwidth}
%% \begin{center}
%%   \raggedright  {\bf  Input:}  NFA \ntbar\  with  underlying
%%   alphabet $\lbrace \acar, \acdr, \bcar, \bcdr\rbrace$ \\
%% %
%%   \raggedright{\bf Output:} NFA  \nt\ with  underlying
%%   alphabet $\lbrace \acar, \acdr \rbrace$ such that
%%   $\lang{\ntbar} \stackrel{*}{\hookrightarrow} \lang{\nt}$.
%%   \\

@@

%%    \STATE $\nt \leftarrow \nt_i$
%%   \STATE delete all edges with label \bcar\ or \bcdr\ in \nt.
%%  \end{algorithmic}
%% \end{center}
%% \end{boxedminipage}
%% \begin{boxedminipage}{.5\textwidth}
%% The algorithm repeatedly introduces  $\epsilon$ edges to bypass a pair
%% of consecutive edges labelled  \bcar\acar\ or \bcdr\acdr.  The process
%% is continued till  a fixed point is reached.  When  the fixed point is
%% reached,   the  resulting   NFA  contains   all   possible  reductions
%% corresponding to all the paths in the original NFA.  The proofs of the
%% termination and correctness of  th The algorithm repeatedly introduces
%% $\epsilon$  edges  to bypass  a  pair  of  consecutive edges  labelled
%% \bcar\acar\  or \bcdr\acdr.   The process  is continued  till  a fixed
%% point is reached.  When the  fixed point is reached, the resulting NFA
%% contains all possible reductions corresponding to all the paths in the
%% original NFA.  The proofs of the termination and correctness of th The
%% algorithm repeatedly  introduces $\epsilon$ edges to bypass  a pair of
%% consecutive edges labelled \bcar\acar\  or \bcdr\acdr.  The process is
%% continued  till a fixed  point is  reached.  When  the fixed  point is
%% reached,   the  resulting   NFA  contains   all   possible  reductions
%% corresponding to all the paths in the original NFA.  The proofs of the
%% termination and correctness of  th The algorithm repeatedly introduces
%% $\epsilon$  edges  to bypass  a  pair  of  consecutive edges  labelled
%% \bcar\acar\  or \bcdr\acdr.   The process  is continued  till  a fixed
%% point is reached.  When the  fixed point is reached, the resulting NFA
%% contains all possible reductions corresponding to all the paths in the
%% original NFA.  The proofs of the termination and correctness of th

%% \end{boxedminipage}
%%  \caption{Algorithm for transforming an NFA to  accept forward
%%    paths only.}\label{algo:simplify-NFA} \figrule
%% \end{figure*}

%% The algorithm repeatedly introduces  $\epsilon$ edges to bypass a pair
%% of consecutive edges labelled  \bcar\acar\ or \bcdr\acdr.  The process
%% is continued till  a fixed point is reached.  When  the fixed point is
%% reached,   the  resulting   NFA  contains   all   possible  reductions
%% corresponding to all the paths in the original NFA.  The proofs of the
%% termination and correctness  of the algorithm are given  in an earlier
%% paper~\cite{karkare07liveness}.

%%\input{liveness-dfa.tex}
\comment{change according  to example} We illustrate  the algorithm in
Figure~\ref{algo:simplify-NFA}  by   constructing  the  automaton  for
\var{\Lanv{9}{y}}.   Figure~\ref{fig:automata-construction}  (c) shows
the  automaton  for  \var{\Lanv{9}{y}}  constructed by  composing  the
automata   for    \var{\Uf{\append}{1}},   \var{\Df{\append}{1}}   and
$(\epsilon \mid \acdr \mid \acdr\acar\sigma_{\mathit{\!all}})$.  After
$\epsilon$ removal we get (d). We add an $\epsilon$ edge from $q_2$ to
$q_3$ bypassing the  \bcdr\acdr\ pair from $q_2$ to  $q_2$ and then to
$q_3$. This  is shown in (e).   The $\epsilon$ edge is  removed in (f)
and  a second  $\epsilon$  is  added to  the  automaton bypassing  the
\bcar\acar\ pair  from $q_1$ to $q_2$.  Removing  this $\epsilon$ edge
gives  the automaton  shown  in (g).   Restricting  this automaton  to
forward edges  only, we  get the final  automaton shown in  (h).  This
automaton  recognizes  $\acdr^{*}\!\mid\acdr^{*}\acar  \sigma_{\mathit
  \!all}$, showing  that the entire list \py,  including its elements,
is live at $\pi_9$. Also note  that the language accepted by the final
automaton satisfies the prefix-closed property.}
\begin{figure}[t!]
\hspace*{1cm}{\epsfig{file=example-automata.eps, height=2.75cm}}
$\caption{(a) The grammar rules for $\Df{\length}{1'}$ converted into
$  an automaton, and simplified in   (b). (c) and (d) show the automata
$  for   \Lanv{9}{\pa}.}
\figrule
\end{figure}

\section{The Garbage Collection Scheme}
% GC assumptions
\cred{Introduction}
